SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-13 frontrunning/Latex/sections/abstract.tex
minor edits + running textidote
grammarly

We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades. Front-running has been an issue in traditional financial instrument markets since the 1970's. With the advent of the blockchain technology, front-running has resurfaced in new forms we explore here, instigated by blockchain's decentralized and transparent nature.
In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 most active decentral applications (DApps) deployed on Ethereum. Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases. Finally, we map proposed solutions to front-running into useful categories. 
\end{abstract}

>>>>

We consider \textit{front-running} to be a course of action where an entity benefits from prior access to privileged market information about upcoming transactions and trades. Front-running has been an issue in financial instrument markets since the 1970s. With the advent of the blockchain technology, front-running has resurfaced in new forms we explore here, instigated by blockchain's decentralized and transparent nature.
In this paper, we draw from a scattered body of knowledge and instances of front-running across the top 25 most active decentral applications (DApps) deployed on Ethereum blockchain. Additionally, we carry out a detailed analysis of \textsf{Status.im} initial coin offering (ICO) and show evidence of abnormal miner's behaviour indicative of front-running token purchases. Finally, we map the proposed solutions to front-running into useful categories. 
\end{abstract}

### 2018-12-13 frontrunning/Latex/sections/paper.tex
grammarly

Blockchain technology enables decentralized applications (DApps) or smart contracts. Function calls (or transactions) to the DApp are processed by a decentralized network. Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized. Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.

The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement. Therefore, DApps need to be studied individually or in categories. In this paper we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps). We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs). Finally, we provide a categorization of  techniques to eliminate or mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.

@@

Cases of front-running are sometimes difficult to distinguish from related concepts like insider trading and arbitrage. In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually gets executed. If the person instead has access to more general privileged information that might predict future transactions, but is not reacting at the actual pending trades, we would classify this activity as insider trading. If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is legal and encouraged because it helps markets integrate new information into prices quickly.

%maybe move this to appendix
\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}. The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily changes the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}. The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W. Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however, differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began regulation. We refer the reader interested in further details on this early regulatory history to Markham~\cite{markham1988front}. The first front-running policies applied only to certain option markets. In 2002, the rule was expanded to cover all security futures~\cite{finra_2002}. In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}. Similar issues have been seen with domain names~\cite{sac022en33:online,edelman2009front} as well.

% we can say other illegal activities in the tranditional system, such as wash trading, ... (notes from AMF) could fall under our definition of front running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades? does it make sense?

@@

In one sense, blockchain technology (introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that participate in a transaction. However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners. Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transactions and broadcast a reactionary transaction that might be confirmed ahead of the original transaction. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textsf{gas}~\cite{AccountT67:online}. The price that users pay for transactions, \textsf{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine. Once seeing two identical transactions with different transaction fees, a rational miner, due to limited space in the blocks, will prioritize the transaction that pays a higher gas price, this is also known as gas auctions~\cite{frontrunme}. Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with a higher gas price. Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.

@@

In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@

As we will illustrate with examples through-out the paper, front-running attacks can often be reduced to one of a few basic templates. First we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks. In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on that contract in that particular state before Alice.

In a \textit{displacement attack}, after Mallory runs her function, Alice's function is either orphaned or runs with no meaningful effect. Examples of displacement include: Alice trying to register a domain name and Mallory registering it first; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{}; and Alice trying to submit a bid in an auction and Mallory copying it. In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first. We call this \textit{asymmetric displacement}. Finally, in some cases, Mallory is trying to run a large set of functions: for example Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain. We call this \textit{bulk displacement}.

@@

The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}.}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface. Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers. 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay. As seen in traditional financial markets, one method to manipulation the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}. As mentioned putting an order in the current decentralized exchange is free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders. The reason for canceling order could be the unprofitability of the order due to price change. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{\todo{cancellation grief}}. This is illustrated in Figure~\ref{fig:MinerFrontrunning}.

@@

Bancor is another DApp that allows users to exchange their tokens without any counter-party risk. The protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}. Smart tokens are ERC20-compatible that can be bought or sold through a DApp-based dealer that is always available and implements a market scoring rule to manage its prices. Bancor provides continuous liquidity for digital assets without relying on brokers to match buyers with sellers. Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the chain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block. This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favourable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}. Researchers have shown and implemented a proof of concept code to front-run Bancor as a non-miner user~\cite{NewTab13:online}.

@@

We classify this in the unique category of a suppression attack in our taxonomy (see Section~\ref{sec:taxonomy}). At first glance, it seemed like an asymmetric/bulk displacement attack on any new ticket purchase transactions. However the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well. Thus, front-running in this case is not the end-goal of the adversary, the way it is in each other category, but is rather a means to an end.

@@

\subsection{Data Collection and Analysis}
According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started. When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network. They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

@@

As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks. Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack. A particular system may implement more than one in a layered mitigation approach.

We classify the mitigations into three main categories. In the first category, the blockchain removes the miner's ability to arbitrarily order transactions and tries to enforce some ordering, or queue, for the transactions. In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on. In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations. We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent. We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.

@@

One alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin does not have a front-running problem for standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

Finally, transactions themselves could enforce order. For example, they could specify the current state of the contract as the only state to execute on. This transaction chaining only prevents certain types of front-running; \ie it prevents insertion attacks but not displacement attacks (recall our taxonomy in Section~\ref{sec:taxonomy}). As transaction chaining only allows one state-changing transaction per state, at most one of a set of concurrent transactions can be confirmed.

@@

All transaction details in Bitcoin are make public and participant identities are only lightly protected. A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,cryptoeprint2015,sasson2014zerocash} for cryptocurrencies. A current research direction is extending these protections to DApps~\cite{aztec2018,ZoeEth2017}. It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running. However there are some nuances here to explore.

A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender. Confidentiality applied to a DApp could mean different levels of protection for each of these. For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2). Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).

The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base. For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party. A DApp could disintermediate this trusted party. Users whose balances are effected by changes in the contract's state would need to be able to learn this information. Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information. As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.

%Shayan: maybe just a reference ^ suffices! 
%A recent attempt to build confidential transactions for DApps, is AZTEC protocol~\cite{aztec2018}. Similar to ZCash ~\cite{hopwood2016zcash}, it uses the concept of encrypted ‘notes’ and join-split transactions. ZCash uses two distinct types of addresses, transparent and shielded addresses, where in AZTEC, user transfers her ERC20 tokens into encrypted notes. Users can transfer these notes by destroying the unspent notes and creating new notes for the new owners, where the sum of the old notes should be equal to the sum of the new notes. 
%Shayan: Talk about AZTEC confidential transactions and their approach for CT. it will be possible to do dark pool style transactions within Ethereum dapps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?). https://medium.com/aztec-protocol/confidential-transactions-have-arrived-a-dive-into-the-aztec-protocol-a1794c00c009

@@

While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal. The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in sequence of functions to be executed. Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).

@@

An early application of this scheme to blockchain is Namecoin, a Bitcoin-forked DApp for name services~\cite{kalodner2015empirical}. In Namecoin, a user sends a commit transaction which registers a new hidden domain name, similar to a sealed bid. Once this first transaction is confirmed, a time delay begins. After the delay, a second transaction reveals the details of the requested domain. This prevent front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.

Commit/reveal is a two round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols). For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all. She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points (flash orders or pinging). If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer. One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}). Finally we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.

@@

Malinova and Park discuss similar design consideration for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}. They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers. To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behaviour, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.

>>>>

Blockchain technology enables decentralized applications (DApps) or smart contracts. Function calls (or transactions) to the DApp are processed by a decentralized network. Transactions are finalized in stages: they (generally) first relay around the network, then selected by a miner and put into a valid block, and finally, the block is well-enough incorporated that is unlikely to be reorganized. Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.

The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or as any mitigations it might implement. Therefore, DApps need to be studied individually or in categories. In this paper, we draw from a scattered body of knowledge regarding front-running attacks on blockchain applications and proposed solutions, with series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps). We do case studies on decentralized exchanges (\eg Bancor), crypto-collectibles (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs). Finally, we provide a categorization of techniques to eliminate or mitigate front-running including transaction sequencing, cryptographic techniques like commit/reveal, and redesigning the functioning of the DApp to provide the same utility while removing time dependencies.

@@

Cases of front-running are sometimes difficult to distinguish from related concepts like insider trading and arbitrage. In front-running, a person sees a concrete transaction that is set to execute and reacts to it before it actually gets executed. If the person instead has access to more general privileged information that might predict future transactions but is not reacting at the actual pending trades, we would classify this activity as insider trading. If the person reacts after the trade is executed, or information is made public, and profits from being the fastest to react, this is considered arbitrage and is legal and encouraged because it helps markets integrate new information into prices quickly.

%maybe move this to appendix
\subsection{Literature on Traditional Front-running}\label{traditionalFrontrunning}
Front-running originates on the Chicago Board Options Exchange (\textit{CBoE}) \cite{markham1988front}. The Securities Exchange Commission \textit{(SEC)} in 1977 defines it as: ``The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{A block in the stock market is a large number of shares, 10\,000 or more, to sell which will heavily change the price.} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades.~\cite{sec1978optionsmarket}'' Self-regulating exchanges (\eg \textit{CBoE}) and the \textit{SEC} spent the ensuing years planning how to detect and outlaw front-running practices~\cite{markham1988front}. The \textit{SEC} stated: ``It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge.\footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities, and Exchange Commission to Joseph W. Sullivan, President  CBoE).}'' The \textit{CBoE} tried to educate their members on existing rules, however, differences in opinion regarding the unfairness of front-running activities, insufficient exchange rules and lack of a precise definition in this area resulted in no action~\cite{sec1978optionsmarket} until the SEC began regulation. We refer the reader interested in further details on this early regulatory history to Markham~\cite{markham1988front}. The first front-running policies applied only to certain option markets. In 2002, the rule was expanded to cover all security futures~\cite{finra_2002}. In 2012, it was expanded further with the new amendment, FINRA Rule 5270, to cover trading in options, derivatives, or other financial instruments overlying a security with only a few exceptions~\cite{sec2012frontrunning,finra_2012}. Similar issues have been seen with domain names~\cite{sac022en33:online,edelman2009front} as well.

% we can say other illegal activities in the traditional system, such as wash trading, ... (notes from AMF) could fall under our definition of front-running on blockchain apps, as the transparency and public nature of the transactions could result in any actor to be involved in such trades? does it make sense?

@@

In one sense, blockchain technology (introduced via Bitcoin in 2008~\cite{nakamoto2008bitcoin}) strives to disintermediate certain central parties that participate in a transaction. However, blockchains also introduce new participants in the relaying and finalization (\ie mining) of transactions that can act as front-runners. Any user monitoring blockchain network transactions (\eg running a full node) can see an unconfirmed transaction and broadcast a reactionary transaction that might be confirmed ahead of the original transaction. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network and listen to the network to monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textsf{gas}~\cite{AccountT67:online}. The price that users pay for transactions, \textsf{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine. Once seeing two identical transactions with different transaction fees, a rational miner, due to limited space in the blocks, will prioritize the transaction that pays a higher gas price, this is also known as gas auctions~\cite{frontrunme}. Therefore, any regular user who runs a full-node Ethereum client can front-run pending transactions by sending similar transaction with a higher gas price. Also, blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textsf{transaction reordering} attack.

@@

In the cryptographic literature, front-running attacks are modeled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@

As we will illustrate with examples throughout the paper, front-running attacks can often be reduced to one of a few basic templates. First, we consider what the adversary is trying to accomplish (without worrying about how) and we distinguish three cases: displacement, insertion, and suppression attacks. In all three cases, Alice is trying to invoke a function on a contract that is in a particular state, and Mallory will try to invoke her own function call on that contract in that particular state before Alice.

In a \textit{displacement attack}, after Mallory runs her function, Alice's function is either orphaned or runs with no meaningful effect. Examples of displacement include: Alice trying to register a domain name and Mallory registering it first; Alice trying to submit a bug to receive a bounty and Mallory stealing it and submitting it first~\cite{}; and Alice trying to submit a bid in an auction and Mallory copying it. In some cases, Alice's function and Mallory's function are different: \eg Alice trying to cancel an offer and Mallory fulfilling the offer first. We call this \textit{asymmetric displacement}. Finally, in some cases, Mallory is trying to run a large set of functions: for example, Alice and others are trying to buy a limited set of shares offered by a firm on a blockchain. We call this \textit{bulk displacement}.

@@

The first category of DApp in Table~\ref{tab:top25DApps} is exchanges. Exchanges such as EtherDelta\footnote{Also known as ForkDelta for the UI \url{https://forkdelta.app/}.}, purport to implement a decentralized exchange, however, their order books are stored on a central server they control and shown to their users with a website interface. Central exchanges can front-run orders in the traditional sense, as well as re-order or block orders on their servers. 0xProtocol~\cite{warren20170x} uses \textit{Relayers} which act as the order book holders and could front-run the orders they relay. As seen in traditional financial markets, one method to manipulation the spot price of an asset is to flood the market with orders and cancel them when there are filling orders --taker's griefing~\cite{consesnsys0xReview2017}. As mentioned putting an order in the current decentralized exchange is free, but to prevent taker's griefing attacks, the user needs to send a transaction to cancel each of his orders. The reason for canceling order could be the unprofitability of the order due to price change. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled, this is known as \textit{\todo{cancellation grief}}. This is illustrated in Figure~\ref{fig:MinerFrontrunning}.

@@

Bancor is another DApp that allows users to exchange their tokens without any counter-party risk. The protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}. Smart tokens are ERC20-compatible that can be bought or sold through a DApp-based dealer that is always available and implements a market scoring rule to manage its prices. Bancor provides continuous liquidity for digital assets without relying on brokers to match buyers with sellers. Implemented on the Ethereum blockchain, when transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the chain (unlike other existing decentralized exchanges), these transactions are all visible to the public for some time before being included within a block. This leaves Bancor vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions, in which they can gain favorable profits by buying before the order and fill the original order with slightly higher price~\cite{BancorIs7:online}. Researchers have shown and implemented a proof of concept code to front-run Bancor as a non-miner user~\cite{NewTab13:online}.

@@

We classify this in the unique category of a suppression attack in our taxonomy (see Section~\ref{sec:taxonomy}). At first glance, it seemed like an asymmetric/bulk displacement attack on any new ticket purchase transactions. However, the key difference is that the front-runner does not care about the execution of her transactions---if miners mined empty blocks for three minutes, that would be fine as well. Thus, front-running, in this case, is not the end-goal of the adversary, the way it is in each other category but is rather a means to an end.

@@

\subsection{Data Collection and Analysis}
According to the analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started. When the ICO opened, F2Pool constructed 31 transactions to the ICO smart contract from these new address, without broadcasting the transactions to the network. They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

@@

As we studied front-running attacks on the blockchain, we also encountered a number of ways of preventing, detecting or mitigating front-running attacks. Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack. A particular system may implement more than one in a layered mitigation approach.

We classify the mitigations into three main categories. In the first category, the blockchain removes the miner's ability to arbitrarily order transactions and tries to enforce some ordering, or queue, for the transactions. In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on. In the final category, DApps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations. We also note that for DApps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent. We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.

@@

One alternative is to sequence transactions pseudorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin does not have a front-running problem for standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

Finally, the transactions themselves could enforce an order. For example, they could specify the current state of the contract as the only state to execute on. This transaction chaining only prevents certain types of front-running; \ie it prevents insertion attacks but not displacement attacks (recall our taxonomy in Section~\ref{sec:taxonomy}). As transaction chaining only allows one state-changing transaction per state, at most one of a set of concurrent transactions can be confirmed.

@@

All transaction details in Bitcoin are made public and participant identities are only lightly protected. A number of techniques increase confidentiality~\cite{bunzBulletproofs,maxwell2015confidential} and anonymity ~\cite{miers2013zerocoin,cryptoeprint2015,sasson2014zerocash} for cryptocurrencies. A current research direction is extending these protections to DApps~\cite{aztec2018,ZoeEth2017}. It is tempting to think that a confidential DApp would not permit front-running, as the front-runner would not know the details of the transaction she is front-running. However, there are some nuances here to explore.

A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender. Confidentiality applied to a DApp could mean different levels of protection for each of these. For front-running, function calls (3,4) are the most important, however, function calls could be inferred from state changes (2). Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).

The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base. For example, one method used by traditional financial exchanges in dealing with front-running from high-frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party. A DApp could disintermediate this trusted party. Users whose balances are affected by changes in the contract's state would need to be able to learn this information. Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information. As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.

%Shayan: maybe just a reference ^ suffices! 
%A recent attempt to build confidential transactions for DApps is AZTEC protocol~\cite{aztec2018}. Similar to ZCash ~\cite{hopwood2016zcash}, it uses the concept of encrypted ‘notes’ and join-split transactions. ZCash uses two distinct types of addresses, transparent and shielded addresses, wherein AZTEC, the user transfers her ERC20 tokens into encrypted notes. Users can transfer these notes by destroying the unspent notes and creating new notes for the new owners, where the sum of the old notes should be equal to the sum of the new notes. 
%Shayan: Talk about AZTEC confidential transactions and their approach for CT. it will be possible to do dark pool-style transactions within Ethereum DApps however they would still expose some information such as sender, receiver (exposes 5,6), hides (3,4?). https://medium.com/aztec-protocol/confidential-transactions-have-arrived-a-dive-into-the-aztec-protocol-a1794c00c009

@@

While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective and is, in fact, an example of an older cryptographic trick known as commit/reveal. The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in a sequence of functions to be executed. Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place it was given (or, generally speaking, not at all).

@@

An early application of this scheme to blockchain is Namecoin, a Bitcoin-forked DApp for name services~\cite{kalodner2015empirical}. In Namecoin, a user sends a commit transaction which registers a new hidden domain name, similar to a sealed bid. Once this first transaction is confirmed, a time delay begins. After the delay, a second transaction reveals the details of the requested domain. This prevents front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.

Commit/reveal is a two-round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols). For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all. She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behavior in traditional financial markets where high-frequency traders will make and cancel orders at many price points (flash orders or pinging). If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer. One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}). Finally, we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.

@@

Malinova and Park discuss similar design consideration for financial markets and trading platforms to mitigate front-running~\cite{malinova2017market}. They model indirect trading costs on search and trading at decentralized exchanges to make front-running costly and inefficient. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers. To prevent front-running, the liquidity demander offers the liquidity-providing trader an incentive; establishing an equilibrium behavior, in which front-runner needs to pay more incentives to come in front of the original trade, making front-running not too profitable.
